\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontspec}

\setmainfont{Roboto}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

% Section formatting
\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}
  [\titlerule]

% Bullet style
\setlist[itemize]{noitemsep, topsep=2pt}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\Huge \textbf{RACIM LONGOU}}\\[6pt]
    \textbf{Computer Engineering Student | Web Developer | Sales Prospecting}\\[6pt]
    Birkhadem, Algiers \;|\;
    \href{mailto:racim.longou@gmail.com}{racim.longou@gmail.com} \;|\;
    +213 55 48 84 34 \;|\;
    \href{https://linkedin.com/in/racim-longou-9a378827a}{linkedin.com/in/racim-longou}
\end{center}

\vspace{6pt}

% ===== PROFESSIONAL SUMMARY =====
\section*{PROFESSIONAL SUMMARY}
Computer engineering student with hands-on experience in web development, software solutions, and client relations. Skilled at analyzing requirements, building functional applications, and coordinating with clients and partners. Interested in software development, IT systems, and technical project management.

% ===== WORK EXPERIENCE =====
\section*{WORK EXPERIENCE}

\textbf{LunchBox} – Chéraga, Algeria \hfill 2023 -- Present\\
Food production – Frozen products and meat processing
\begin{itemize}
    \item Prospect and manage a B2B client portfolio.
    \item Analyze client needs and handle business negotiations.
    \item Internship (April -- July 2025): Developed a web application for stock and employee management.
    \item Implemented an internal system to improve product tracking and workflow.
\end{itemize}

\textbf{Tradal Auto} – Algeria \hfill 2024\\
Car dealership – Vehicle sales and rentals
\begin{itemize}
    \item Designed and developed the company’s main website.
    \item Assisted with client prospecting and business development.
    \item Enhanced digital visibility and online presentation of vehicles.
\end{itemize}

\textbf{Winover} – Chéraga, Algiers \hfill 2025\\
Software development and IT systems
\begin{itemize}
    \item Contributed to web development and external communications.
    \item Participated in professional software projects.
    \item Provided technical support and contributed to discussions on upcoming digital projects.
\end{itemize}

\textbf{Djezzy} – Dar El Beïda, Algeria \hfill April -- July 2026\\
Telecommunications operator
\begin{itemize}
    \item Internship developing a digital payment solution.
    \item Participated in technical design and module implementation.
\end{itemize}

% ===== EDUCATION =====
\section*{EDUCATION}
\textbf{CESI – Engineering School} \hfill Ongoing\\
Computer Engineering (3-year program)

% ===== SKILLS =====
\section*{SKILLS}
\begin{itemize}
    \item Web Development: HTML, CSS, JavaScript, PHP, MySQL
    \item Networking and IT systems
    \item Technical project management
    \item Client prospecting and professional communication
\end{itemize}

% ===== CERTIFICATIONS =====
\section*{CERTIFICATIONS}
\begin{itemize}
    \item Cisco Certified Network Associate (CCNA) – 2025
\end{itemize}

\end{document}
